A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-18 paper/refactor.tex
first essay for method-text for handpicked concepts

Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.
\input{handpicked_table}
\section{Results}

>>>>

Based on this definition, we evaluate the resultant \textit{top senses} of some texts and then check the results of the different similarities with well known concepts in the next sections.

The selected concepts are shown in the table below. We can distinguish three subsets in this selection: concepts related to practical situations like geopolitics and state management (like ...), concepts more related to the theoretical world (like...) and finally, concepts not related to Lenin works (like...). The motivation behind the selection of the two first groups is to check some easy hipotheses (such as "State and Revolution" talk a lot about "state" and "revolution", the motivation behind the third group is to chenk our methods for false positives, i.e., a high ranking in our metrics for a concept assumed not related to the works.

\input{handpicked_table}
\section{Results}
